Secure Composition of Robust and Optimising Compilers

### 2023-06-15 popl/main.tex
contrib

\BrText{Validation}{In summary, this paper makes the following contributions:

\begin{itemize}
  \item %
        %\Cref{sec:compprop} presents a formal framework to reason about compositions of security properties and demonstrate its usage with concrete examples:
        A formal framework to reason about the composition of security properties (\Cref{sec:compprop}).
        %Given a most general trace model, we define the trace-based security properties \gls{tms}, \gls{sms}, \gls{ms}, \gls{cct}, and their compositions.
        Using the framework, the ease for formal reasoning with compositions of security properties is demonstrated by instantiating the framework on \gls{tms}, \gls{sms}, and \gls{cct}, which are ultimately composed to \gls{ms} and a combination of \gls{ms} and \gls{cct}.
        %For each of these properties, we also give a monitor which runs on another trace model that excludes unneccessary information and show that their composition is behaviorally similar to the composition of the trace-based security properties.
        %This two-level approach enhances modularity: When working with the security properties, one only needs to reason about the corresponding monitor.
        %%% let's omit above sentences completely. why ramble about monitors in the introduction? this ain't about model checking

  \item %
        %\Cref{sec:compcomp} studies different forms of secure compiler compositions.
        Foundational, theoretical work on different forms of compositions of secure compilers (\Cref{sec:compcomp}).
        %Concretely, it investigates upper and lower compositions, as well as the sequential composition.
        First, this paper proves theorems which state that a compiler with multiple input or output languages is secure as long as the compiler is composed of several secure passes with one input and one output language, respectively.
        Second, a theorem about the sequential composition of secure compilers is proven, which states that sequentially composing secure compilers is, again, secure with respect to the composition of the properties they preserve.
        %A simple corollary of sequential composition is the ability to freely reorder compiler optimizations without compromising security.

  \item %
        % \Cref{sec:casestud} sets up a case-study to demonstrate the power of our formal framework.
        A case-study demonstrating the power of the formal frameworks from the previous contributions (\Cref{sec:casestud}).
        %We define several different languages and compilers between them and prove that the compilers are robustly preserving different properties.
        To this end, a compilation chain of several passes is presented.
        %The sequential composition of these compilers yields a compilation chain that is optimizing and robustly preserving a combination of \gls{ms} and \gls{cct}.
        The chain attains a combination of \gls{ms} and \gls{cct} by means of applying the theoretical work from the previous contribution on the individual, secure passes concerning \gls{tms}, \gls{sms}, and \gls{scct}, respectively.
        %As for optimizations, the chain has two passes, one performing \gls{cf} and the other \gls{dce}.
        Furthermore, the chain entails two passes for \gls{ms}\MKin{maybe patch \gls{ms} when optimizing passes are done} that are optimizing: One performs a simple \gls{dce} and the other \gls{cf}.
        %This compilation chain demonstrates the ability to perform modular proof engineering by leaveraging this paper's compositionality theorems.
        This demonstrates that the usage of the presented framework is both simpler and more expressive compared to one monolithic security proof of the whole compilation chain.

  \item The key contributions are formalized in the Coq proof assistant.
        The practically relevant parts of the formalization are \emph{extractable}.
        That is, one can translate the Coq code to Ocaml and run the compilation chain from the previous contribution.
        Finally, this paper indicates with \CoqSymbol whenever definitions or proofs are done in Coq.
\end{itemize}}

%In \Cref{sec:background}, the paper establishes the notions of traces, (hyper-)properties, and robust preservation, while \Cref{sec:relwork} compares this work with others.
For the other parts of the paper, the notions of security properties and secure compilers are introduced (\Cref{sec:background}).
%We conclude in \Cref{sec:concl} and give an outlook for future work.
The work presented in this paper is compared to others from the literature (\Cref{sec:relwork}) and there is a conclusion with an outlook for future work (\Cref{sec:concl}).

>>>>

% \BrText{Validation}{
In summary, this paper makes the following contributions:

\begin{itemize}
  \item %
        %\Cref{sec:compprop} presents a formal framework to reason about compositions of security properties and demonstrate its usage with concrete examples:
        First, this paper studies the formalisation and the composition of security properties (\Cref{sec:compprop}) by focussing on those safety properties that are of interest for real-world compiler writers (as identified by the plethora of work enforcing such properties individually~\MP{cits}).
        % 
        Starting from ways to formalise and enforce those properties individually, this paper shows how to compose both their formalisation and their composition.
        % 
        This paper then showcases the benefits of this composition by composing \gls{tms} and \gls{sms} into \gls{ms}, and ultimately adding \gls{cct} to the composition, yielding the the conjunction of \gls{ms} and \gls{cct}.
        % 
        The resulting security property is the golden standard of safety properties that secure cryptographic code should have~\MP{cits}.
        \MPin{
        	conclude that did this prop in a single pass, we show how to do it compositionally
        }
        %For each of these properties, we also give a monitor which runs on another trace model that excludes unneccessary information and show that their composition is behaviorally similar to the composition of the trace-based security properties.
        %This two-level approach enhances modularity: When working with the security properties, one only needs to reason about the corresponding monitor.
        %%% let's omit above sentences completely. why ramble about monitors in the introduction? this ain't about model checking

  \item %
        %\Cref{sec:compcomp} studies different forms of secure compiler compositions.
        This paper takes the secure compilation framework of~\citep{abate2019jour} and extends it to reason about the security of all different known forms of compiler composition (\Cref{sec:compcomp}).
        %Concretely, it investigates upper and lower compositions, as well as the sequential composition.
        For this, this paper studies \MP{}.
        % 
        This paper proves that starting from two compilers that preserve two properties, their composition preserves the intersection of those properties.
        \MPin{
       		find way to connect to previous contrib
        }
        % 
        Finally, this paper provides a simple but crucial corollary that demonstrates that the order of composition of sequential compiler passes is irrelevant for the resulting security.
        % 
        This corollary is crucial for reordering compiler optimisation passes as well as secure compilation passes and thus generating secure and efficient code.

  \item %
        % \Cref{sec:casestud} sets up a case-study to demonstrate the power of our formal framework.
        This paper presents a case-study showcasing the conjunction of the previous contributions (\Cref{sec:casestud}).
        %We define several different languages and compilers between them and prove that the compilers are robustly preserving different properties.
        To this end, it presents a compilation chain consisting of several passes.
        %The sequential composition of these compilers yields a compilation chain that is optimizing and robustly preserving a combination of \gls{ms} and \gls{cct}.
        The chain ultimately preserves a combination of \gls{ms} and \gls{cct} by means of composing the individual, secure passes concerning \gls{tms}, \gls{sms}, and \gls{scct}, respectively.
        %As for optimizations, the chain has two passes, one performing \gls{cf} and the other \gls{dce}.
        Furthermore, the chain includes two passes for \gls{ms}\MKin{maybe patch \gls{ms} when optimizing passes are done} that are optimizing: One performs a simple \gls{dce} and the other \gls{cf}.
        %This compilation chain demonstrates the ability to perform modular proof engineering by leaveraging this paper's compositionality theorems.
        This demonstrates that the usage of the presented framework is both simpler and more expressive compared to one monolithic security proof of the whole compilation chain.
        \MP{ matthis please write your idea here }

  \item The key contributions are formalized in the Coq proof assistant.
        The practically relevant parts of the formalization are \emph{extractable}.
        That is, one can translate the Coq code to Ocaml and run the compilation chain from the previous contribution.
        Finally, this paper indicates with \CoqSymbol whenever definitions or proofs are done in Coq.
\end{itemize}
% }

%In \Cref{sec:background}, the paper establishes the notions of traces, (hyper-)properties, and robust preservation, while \Cref{sec:relwork} compares this work with others.
This paper starts by introducing relevant notions of security properties and secure compilation (\Cref{sec:background}),
%We conclude in \Cref{sec:concl} and give an outlook for future work.
and discusses related work (\Cref{sec:relwork}) before concluding (\Cref{sec:concl}).
